Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-25 latex/afm-cs-main.tex
Update on Overleaf.

In order to minimize the scanning time, tip tip should be moved as fast as possible when trainsitioning between $\mu$-path locations (state (1)). Since such speeds can be beyond the bandwidth of the $z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip sear and sample damage. In our initial implementation, this was achieved by 
%In our initial implementation
\cite{braker_hardware_2018}, we insisted that the during
tip-retraction (state (5)), the cantilever tip should fully break
contact with the surface. Here, we impose no such requirement. Rather,
we change the $Z$-setpoint during tip-retraction to only pull away far
enough that the deflection signal stays low (i.e., below the scanning
setpoint), even while we run across the surface. We choose \rzup so
that the interaction between the tip and sample becomes purely
adhesive. In general, stable imaging is not possible at \rzup and
complete dis-engagement occasionally occurs. This can be seen in bottom pane of
Fig.~\ref{fig:cs_cycle} during the second $XY$-move (black portion) where the tip detaches partway through the move.
%Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$ based the current state.
When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme to prevent the control from saturating.

Only moving the tip into the adhesive region during the $XY$ move saves considerable time
compared to completely detaching the tip between each $\mu$-path. By eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality. However, completely characterizing the damage done to the tip and sample with this scheme compared complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the AFM control loop for all three axes.
    Not shown is anti-windup for the $Z$-axis integrator, which is active
    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. More
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_x}{z-1}\right\rceil
\end{equation}
time steps, where $H_x$ is closed-loop transfer function for the
$x$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.

>>>>

In order to minimize the scanning time, tip tip should be moved as fast as possible when trainsitioning between $\mu$-path locations (state (1)). Since such speeds can be beyond the bandwidth of the $z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip wear and sample damage. In our initial implementation \cite{braker_hardware_2018}, 
%we insisted that the during
this was achieved by insisting that during the
tip-retraction (state (5)), the cantilever tip should fully break
contact with the surface. Here, we impose no such requirement. Rather,
we change the $Z$-setpoint during tip-retraction to only pull away far
enough that the deflection signal stays low (i.e., below the scanning
setpoint), even while we run across the surface. We choose \rzup so
that the interaction between the tip and sample becomes purely
adhesive. In general, stable imaging is not possible with the setpoint at \rzup and
complete dis-engagement occasionally occurs. This can be seen in the bottom pane of
Fig.~\ref{fig:cs_cycle} during the second $XY$-move (black portion) where the tip detaches partway through the move.
%Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$ based the current state.
When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme to prevent the control from saturating.

Only moving the tip into the adhesive region during the $XY$ move saves considerable time
compared to completely detaching the tip between each $\mu$-path. By essentially eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality and is a key component to the new quality metric we introduce in Sec.~\ref{sec:rdi}. However, completely characterizing the damage done to the tip and sample with this scheme compared complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
  \caption{Block diagram of the AFM control loop for all three axes.
    Not shown is anti-windup for the $Z$-axis integrator, which is active
    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
  \label{fig:afm_bd_dinv}
\end{figure*}
\subsection{The pre-scan}
After the tip-descent, we begin scanning in a ``pre-scan'' phase
(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
have observed that there is less noise in the deflection signal while
the $XY$-stage is in motion compared to sitting still. Second, and more
importantly, it lets us bring the $X$-axis to its scanning velocity at
the same time the transients from the $Z$-axis die out. Without this,
we must extend the $\mu$-path by a distance equal to the steady-state
error following a ramp. For an arbitrary scan speed, this means the
$\mu$-path scan would need an extra
\begin{equation}
  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_x}{z-1}\right\rceil
\end{equation}
time steps, where $H_x$ is closed-loop transfer function for the
$x$-axis. For our system $N=111$. By initiating the scan while the
$Z$-axis settles, we eliminate much of this overhead.
